### 2021-07-11 src/paper/results/share_known_cases.tex
Make share of detected cases results section ready for review.

\subsection{Share of Cases that are Detected}
\label{subsec:appendix_share_known_cases}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/share_known_cases/full_combined_baseline_by_age_group_rki}
  \caption{Share of Detected Cases by Age Group}
  \label{fig:share_known_cases_by_age_group}
  \floatfoot{\noindent \textit{Note:} The figure shows the share of cases that is
  reported as an official case via PCR confirmation. We use the overall share of known
  cases that was estimated through the case fatality ratio by the
  \href{https://covid19.dunkelzifferradar.de/}{Dunkelzifferradar} for all of 2020 and
  then assume it to be constant as vaccinations of the elderly strongly affect the case
  fatality rate which the project does not account for. To get from an overall share of
  detected cases to the share of cases that is detected in each age group we use that
  asymptomatic cases are much less likely to be detected. As our model covers age
  specific asymptomatic rates this endogenously leads to group specific share known cases
  that verify that infections in younger age groups are under-detected. Starting in 2021
  in addition to the overall numbers of detected cases through symptoms and the share
  known cases, cases are also detected through confirmation of positive rapid tests. This
  leads to an increase in the share of known cases for all age groups but in particular
  for the younger age groups that are covered extensively with rapid tests through the
  rapid test requirement for participating in school.}
\end{figure}

It's noteworthy that the share of detected cases increases rapidly in May for the five to
fourteen year olds. This is a direct result of the mandatory tests in
school.

>>>>

\subsection{Share of Detected Cases}
\label{subsec:results_share_known_cases}

We show the age group specific share of detected cases in
Figure~\ref{fig:share_known_cases_by_age_group}.\footnote{We explain how we model the
detection of cases in Section~\ref{sub:testing} and show the overall share of detected
cases that we use as input for our testing model in
Section~\ref{subsec:data_share_known_cases}.}

In 2020 the share of detected cases is much higher in older age groups as they are much
more likely to develop symptoms and symptomatic individuals are much more likely to be
tested. Starting in 2021 the share of detected cases not only depends on the overall
share of detected cases we feed into our model but also on the number of performed rapid
tests. As more and more (often asymptomatic and presymptomatic) individuals receive
positive rapid tests and receive confirmation, the share of detected cases starts to
increase, especially after March when rapid tests became much more widely available. This
effect is very visible for school pupils, (5-14, green line). As twice weekly rapid tests
become mandatory in schools and students start going to school after the Easter break,
the share of detected cases for that group increases drastically from 25\% to over 60\%
between April and June.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.5\textwidth]{figures/results/figures/share_known_cases/full_combined_baseline_by_age_group_rki}
  \caption{Share of Detected Cases by Age Group}
  \label{fig:share_known_cases_by_age_group}
  \floatfoot{\noindent \textit{Note:} The figure shows the share of cases that is
  reported as an official case via PCR confirmation for each age group in our population.
  We use the overall share of detected cases that was estimated through the case fatality
  ratio by \citet{Dunkelzifferradar2020} for all of 2020 and then assume it to be
  constant as vaccinations of the elderly strongly affect the case fatality rate which
  the project does not account for. To get from an overall share of detected cases to the
  share of cases that is detected in each age group we use that asymptomatic cases are
  much less likely to be detected. As our model covers age specific asymptomatic rates
  this endogenously leads to group specific share of detected cases that suggest that
  infections in younger age groups are under-detected. Starting in 2021 in addition to
  the overall numbers of detected cases through symptoms and the share of detected cases,
  cases are also detected through confirmation of positive rapid tests. This leads to an
  increase in the share of detected cases for all age groups but in particular for the
  younger age groups that are covered extensively with rapid tests through the rapid test
  requirement for participating in school. Age groups that have a high share of workers
  also disproportionately increase their detection rate.}
\end{figure}
